Depression and suicidality as costly signals of need

### 2021-03-22 Paper.rmd
added some notes to the RMD
Added emotion heatmaps

tar_load(
  c(
    'd',
    'models',
    'models_prereg',
    'effectsPlots', 
    'plot_T1Belief_T1Action',
    'plot_emotions',
    'plot_raw_beliefs',
    'plot_raw_actions',
    'med1b',
    'm1b_boot',
    'm3b_boot'
    )
  )

@@

Scenarios likely favor cheating due to high potential of benefits
## Limitations

@@

>>>>

tar_load(
  c(
    'd',
    'models',
    'models_prereg',
    'effectsPlots', 
    'plot_T1Belief_T1Action',
    'plot_emotions',
    'plot_raw_beliefs',
    'plot_raw_actions',
    'med1b',
    'm1b_boot',
    'm3b_boot',
    'plot_T1emotion_heatmap',
    'plot_T2emotion_heatmap'
    )
  )

@@

Scenarios likely favor cheating due to high potential of benefits

## Limitations

@@

## T1 emotion vs vignette heatmap

```{r t1emotionheatmap, fig.width=8, fig.cap="Time 1 inference of victim's emotional state in each vignette. Each cell represents the proportion of participants who inferred that emotion. Participants could check multiple emotions from the list."}
plot_T1emotion_heatmap
```

## T2 emotion vs signal heatmap

```{r t2emotionheatmap, fig.width=8, fig.cap="Time 2 inference of victim's emotional state following the signal. Each cell represents the proportion of participants who inferred that emotion. Participants could check multiple emotions from the list."}
plot_T2emotion_heatmap
```
